---
title: 'Analysis of SARS-CoV-2 SNP Data'
author: "Kim Medina"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
csl: bioinformatics.csl
bibliography: references.bib
params:
  input_file: "data/sample_snp_data.csv"
  sample_id: "SRR12433063"       
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      error = FALSE)
```

```{r, set-params}
input_file <- params$input_file
sample_id <- params$sample_id
```


## Setup
```{r, assignment-of-SNP-dataset-and-sample-ID-to-variable}
snp_data <- params$input_file
sample_id <- "SRR12433063"
```

```{r, load-packages-and-source-function-file}
library(dplyr)
library(ggplot2)
library(knitr)
source("code/functions/subset_data_function.R")
```

## Project Description

This project analyzes single nucleotide polymorphism (SNP) data from SARS-CoV-2 samples. It subsets the data to focus solely on one sample only. The SNP data is then visualized in a plot. The first package used is dplyr [@dplyr]. Then ggplot2 is used to create the plot [@ggplot2]. Lastly, knitr is used to create the report [@knitr].

## Subsetting data

```{r, writing-csv-file}
single_sample_data <- subset_snp_data(snp_data, sample_id)
output <- paste("output/sample_snp_data_", sample_id, ".csv", sep = "")
write.csv(single_sample_data, file = output, row.names = FALSE)
kable(single_sample_data, caption = paste0("SNP data for sample ", sample_id))
```

## Figure

```{r, plot-quality-across-genome-subset}
snp_data %>%
  subset_snp_data(sample_id) %>%
  ggplot(aes(x = pos,
             y = qual,
             color = sample)) +
  geom_point(size = 3) +
  labs(title = paste0("SNP quality of sample ",
                      sample_id, " across SARS-CoV-2 Genome"),
       x = "Position in Genome (nt)",
       y = "SNP Quality")
ggsave(paste0("output/plot_quality_across_genome_", sample_id, ".png"))
```

```{r, plot-alt-across-genome-subset}
snp_data %>%
  subset_snp_data(sample_id) %>%
  ggplot(aes(x = pos,
             y = alt,
             color = sample)) +
  geom_point(size = 3) +
  labs(title = paste0("Alt SNP of sample ",
                      sample_id, " across SARS-CoV-2 Genome"),
       x = "Position in Genome (nt)",
       y = "Alternative SNP")
ggsave(paste0("output/plot_alt_snp_across_genome_", sample_id, ".png"))
```


### Session Info
```{r, session-info}
devtools::session_info()
```

# Sources Cited
